quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-09 paper-quollr.Rmd
Added the error plot

```{r load-libraries}
library(quollr)
library(tibble)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(patchwork)
library(readr)

@@

scurve_nldr1 <- umap_scaled1 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  theme(aspect.ratio = 1) +
  interior_annotation("a", c(0.08, 0.9))

@@

scurve_nldr2 <- umap_scaled2 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  theme(aspect.ratio = 1) +
  interior_annotation("b")

@@

scurve_nldr3 <- umap_scaled3 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  theme(aspect.ratio = 1) +
  interior_annotation("c", c(0.08, 0.9))

@@

scurve_nldr4 <- umap_scaled4 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  theme(aspect.ratio = 1) +
  interior_annotation("d")

@@

scurve_nldr5 <- umap_scaled5 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#636363') +
  theme(aspect.ratio = 1) +
  interior_annotation("e")

@@

scurve_nldr6 <- umap_scaled6 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#984ea3') +
  theme(aspect.ratio = 1) +
  interior_annotation("f")
```

@@

```{r}
error_plot + wrap_plots(
  scurve_nldr1, scurve_nldr2, 
  scurve_nldr3, scurve_nldr4,
  scurve_nldr5, scurve_nldr6, 
  ncol = 2, widths = c(50, 50))
```

>>>>

```{r load-libraries}
library(quollr)
library(tibble)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(patchwork)
library(readr)
library(tools)

@@

scurve_nldr1 <- umap_scaled1 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("a", c(0.08, 0.9))

@@

scurve_nldr2 <- umap_scaled2 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  interior_annotation("b")

@@

scurve_nldr3 <- umap_scaled3 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  interior_annotation("c", c(0.08, 0.9))

@@

scurve_nldr4 <- umap_scaled4 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("d")

@@

scurve_nldr5 <- umap_scaled5 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#636363') +
  interior_annotation("e")

@@

scurve_nldr6 <- umap_scaled6 |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#984ea3') +
  interior_annotation("f")
```

@@

```{r}
free(error_plot) + wrap_plots(
  scurve_nldr1, scurve_nldr2, 
  scurve_nldr3, scurve_nldr4,
  scurve_nldr5, scurve_nldr6, 
  ncol = 2)
```
